---
title: "Business Intelligence Lab Submission Markdown"
author: "<Specify your group name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Student ID Numbers and Names of Group Members** | *\<list one student name, group, and ID per line; you should be between 2 and 5 members per group\>* |
|                                                   |                                                                                                      |
|                                                   | 1.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 2.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 3.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 4.  ID - Group - Name                                                                                |
|                                                   |                                                                                                      |
|                                                   | 5.  ID - Group - Name                                                                                |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **GitHub Classroom Group Name**                   | Test                                                                                                 |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Code**                                   | BBT4206                                                                                              |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Course Name**                                   | Business Intelligence II                                                                             |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Program**                                       | Bachelor of Business Information Technology                                                          |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+
| **Semester Duration**                             | 21^st^ August 2023 to 28^th^ November 2023                                                           |
+---------------------------------------------------+------------------------------------------------------------------------------------------------------+

# Setup Chunk

**Note:** the following "*KnitR*" options have been set as the defaults:\
`knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy.opts = list(width.cutoff = 80), tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
install.packages("formatR", repos="https://cloud.r-project.org")
library(formatR)
knitr::opts_chunk$set(
	eval = TRUE,
	echo = TRUE,
	warning = FALSE,
	collapse = FALSE,
	tidy = TRUE
)
```

**Note:** the following "*R Markdown*" options have been set as the defaults:

> output:\
> \
> github_document:\
> toc: yes\
> toc_depth: 4\
> fig_width: 6\
> fig_height: 4\
> df_print: default\
> \
> editor_options:\
> chunk_output_type: console

# Loading the Student Performance Dataset

Testing for Group A (loading the student performance dataset).

```{r Your Second Code Chunk}
install.packages("readr", repos="https://cloud.r-project.org")
student_performance_dataset <-
  readr::read_csv("../data/20230412-20230719-BI1-BBIT4-1-StudentPerformanceDataset.CSV",
           col_types =
             readr::cols(
               class_group = readr::col_factor(levels = c("A", "B", "C")),
               gender = readr::col_factor(levels = c("1", "0")),
               YOB = readr::col_date(format = "%Y"),
               regret_choosing_bi = readr::col_factor(levels = c("1", "0")),
               drop_bi_now = readr::col_factor(levels = c("1", "0")),
               motivator = readr::col_factor(levels = c("1", "0")),
               read_content_before_lecture =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               anticipate_test_questions =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               answer_rhetorical_questions =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               find_terms_I_do_not_know =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               copy_new_terms_in_reading_notebook =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               take_quizzes_and_use_results =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               reorganise_course_outline =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               write_down_important_points =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               space_out_revision =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               studying_in_study_group =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               schedule_appointments =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               goal_oriented = readr::col_factor(levels = c("1", "0")),
               spaced_repetition =
                 readr::col_factor(levels = c("1", "2", "3", "4")),
               testing_and_active_recall =
                 readr::col_factor(levels = c("1", "2", "3", "4")),
               interleaving = readr::col_factor(levels = c("1", "2", "3", "4")),
               categorizing = readr::col_factor(levels = c("1", "2", "3", "4")),
               retrospective_timetable =
                 readr::col_factor(levels = c("1", "2", "3", "4")),
               cornell_notes = readr::col_factor(levels = c("1", "2", "3", "4")),
               sq3r = readr::col_factor(levels = c("1", "2", "3", "4")),
               commute = readr::col_factor(levels = c("1", "2", "3", "4")),
               study_time = readr::col_factor(levels = c("1", "2", "3", "4")),
               repeats_since_Y1 = readr::col_integer(),
               paid_tuition = readr::col_factor(levels = c("0", "1")),
               free_tuition = readr::col_factor(levels = c("0", "1")),
               extra_curricular = readr::col_factor(levels = c("0", "1")),
               sports_extra_curricular = readr::col_factor(levels = c("0", "1")),
               exercise_per_week = readr::col_factor(levels = c("0", "1", "2", "3")),
               meditate = readr::col_factor(levels = c("0", "1", "2", "3")),
               pray = readr::col_factor(levels = c("0", "1", "2", "3")),
               internet = readr::col_factor(levels = c("0", "1")),
               laptop = readr::col_factor(levels = c("0", "1")),
               family_relationships =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               friendships = readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               romantic_relationships =
                 readr::col_factor(levels = c("0", "1", "2", "3", "4")),
               spiritual_wellnes =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               financial_wellness =
                 readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               health = readr::col_factor(levels = c("1", "2", "3", "4", "5")),
               day_out = readr::col_factor(levels = c("0", "1", "2", "3")),
               night_out = readr::col_factor(levels = c("0", "1", "2", "3")),
               alcohol_or_narcotics =
                 readr::col_factor(levels = c("0", "1", "2", "3")),
               mentor = readr::col_factor(levels = c("0", "1")),
               mentor_meetings = readr::col_factor(levels = c("0", "1", "2", "3")),
               `Attendance Waiver Granted: 1 = Yes, 0 = No` =
                 readr::col_factor(levels = c("0", "1")),
               GRADE = readr::col_factor(levels = c("A", "B", "C", "D", "E"))),
           locale = readr::locale())
```

Describe the next code chunk here:

```{r Your Third Code Chunk}
summary(student_performance_dataset)
```

## \<You Can Have a Sub-Title Here\>

```{r Your Fourth Code Chunk}
# Fill this with other R related code that will be executed when the R markdown
# file is rendered using knitR
library(readr)
```

# \<You can Provide Another Appropriate Title Here\>

Describe the code chunk here:

```{r Your Fifth Code Chunk}
# Fill this with R related code that will be executed when the R markdown file
# is rendered using knitR
library(readr)
```

**etc.** as per the lab submission requirements.
